\documentclass[stu,12pt]{apa7}
  \usepackage{times}               % Times New Roman Font Face
  \usepackage[american]{babel}      % Localization
  \usepackage[utf8]{inputenc}      % Input Encoding
  \usepackage{hyperref}            % Hyperlinks
  \usepackage{enumitem}            % Additional Enumeration Environment Settings
  \usepackage{geometry}            % Page Layout
  \usepackage{soul}                % Text Highlighting
  \usepackage{graphicx}            % Images
  \usepackage{csquotes}            % Quoting Environment
  \usepackage{bookmark}            % Required by `csquotes'
  \usepackage{mdframed}            % Colorful Tex-Box Environment
  \usepackage[toc]{appendix}       % Appendix
  \usepackage{fancyhdr}            % Headings and Footers
  % \usepackage[%
    % style=apa,%
    % sortcites=true,%
    % sorting=nyt%
  % ]{biblatex}
  \usepackage{xcolor}

  % Bibliography Setup
  %% Language Mappings
  % \DeclareLanguageMapping{english}{english-apa}
  % \DeclareLanguageMapping{american}{american-apa}
  %% Bibliography File Path
  % \addbibresource{main.bib}

  % Hyperlink Setup
  \hypersetup{
    colorlinks = true,
    urlcolor = blue,
    linkcolor = blue,
    citecolor = blue
  }

  % Page and Text Layout
  \geometry{%
    a4paper,%
    top=1in,%
    bottom=1in,%
    left=1in,%
    right=1in%
  }
  \setlength{\headheight}{15pt}

  % Header
  \lhead{COM120CG1-M2D2}

  % Title Page
  \title{%
    M2D2: Improving YOUR Interpersonal Communication Skills
  }
  \shorttitle{Module 2 Discussion 2}
  \author{Ashton Hellwig}
  \authorsaffiliations{Department of Mathematics, Front Range Community College}
  \course{COM115: Interpersonal Communication}
  \professor{Richard Thomas}
  \duedate{November 14, 2020 23:59:59 MDT}
  \date{\today}
  \abstract{%
    \textbf{Overview}\\%
    In Module 1 you committed to becoming a better interpersonal communicator.
      In each module, we will check in to see how those efforts are proceeding.
      In this module, you will report on how your practice has progressed so
      far.\\%

    You should spend approximately 4 hours on this assignment.%
  }

\begin{document}
  % Title Page
  \maketitle

  % Initial Post
  \section{Initial Post}
    \subsection*{Instructions}
      \begin{enumerate}
        \item To assist your classmates, list again the two (2) interpersonal
          communication skills you chose to improve.
        \item Friendly and Important Reminder: Attach to the Main post a
          Microsoft Word document a Progress Report containing detailed practice
          sessions demonstrating attempts to improve the two communication
          skills you have chosen to improve.
          \begin{itemize}
            \item NOTE:\ Sample of how to format your practice log in a Word
              Document. (Click anywhere on the previous sentence to open and
              review the sample).
          \end{itemize}
        \item In the Main post include the following:
          \begin{itemize}
            \item Consider the topic of conflict. Everyone deals with conflict
              situations. Consider how Brooke and Gary dealt with conflict in
              the video. Was their method effective? Why or why not? Use
              evidence from your readings to support your post.
            \item If dealing with conflict or conflict resolution is on your
              list, reflect on what you learned in this module about conflict
              that will help you moving forward. Review what your classmates
              posted about their goals, and choose at least two different people
              who have a goal different from yours. Post a resource that you
              feel will provide a strategy for improving one of their identified
              skills.
            \item If dealing with conflict or conflict resolution is not on your
              list, offer suggestions for at least two other students who are
              trying to improve their skills in the area of conflict. What items
              covered in this module will help your fellow students? Are there
              outside resources or strategies you can share?
          \end{itemize}
        \item When the assignment is completed, you will have submitted a Main
          post and read and replied to the Main post  submitted by two
          classmates.
        \item Continue keeping track of what you practice, when you practice
          (time and date), who you practiced with, what strategies you used when
          you practice, and the outcome of that practice in your Word document.
          Include details with each practice session. You will continue to share
          practice session updates in future Modules. In each Module, continue
          to add practice sessions to the same Word document. Do not start over.
          By the end of the course, all your work should be posted in the same
          Word document. Include an updated Word document with your Main post.
          Again, refrain from starting a new document. We want to see the
          progress you make Module-to-Module.
      \end{enumerate}


    \newpage
    \paragraph{How Effective Were Gary and Brooke at Conflic Resolution?}
      The conversation we witnessed between Gary and Brooke was an excellent
        illustration of poor conflict resolution skills on \textit{both}
        sides. Both parties tended to personally attack one another in terms of
        their personality and character rather than focusing on whatever
        situation prompted the argument. Instead of listening to one-another,
        they simply tried to defend or justify their actions without regard
        to the other's feelings. I actually \textbf{just} met the end of five
        year long relationship, so this module and especially that video were
        an incredibly painful experience for me to undertake and it was
        incredibly unpleasant.

    \paragraph{Progress Report on My Two Skills to Improve}
      The two skills I chose to improve were: obtaining a stronger hold on
        psychological context, and listening during conversation with more of
        an intent to understand rather than to reply. After this module and my
        recent heart-and-world-shattering situation, I would like to replace one
        of those (if I am \textit{only} allowed two) with that of conflict
        resolution and improving my ability in that. I tend to be either
        \textit{too} emotional or appearing \textit{emotionless} depending on
        how defensive I feel during the conversation, I suppose. This goes
        hand-in-hand too, with the proper utilization of \textit{silence}.

      Please see the attached word document


  % Replies
  % \include{tex/01-response.tex}
  % \include{tex/02-response.tex}

  % Bibliography
  %% Works Cited
  % \newpage
  % \printbibliography[%
    % title={Works Cited},%
    % heading={bibintoc},%
    % notcategory={consulted}%
  % ]

  %% Works Consulted
  % \newpage
  % \nocite{*}
  % \printbibliography[%
    % title={Works Consulted},%
    % heading={bibintoc},%
    % category={consulted}%
  % ]
\end{document}
